Demo: Counterpoint by Construction

### 2019-05-26 doc/farm/farm-abstract.tex
typo
added some more code

As an example, the simplest of Fux's rule systems is first-species
counterpoint, in which one starts with a base melody (the \textit{cantus firmus})
and contructs a counterpoint melody note-by-note in the same rhythm.
``Dissonant'' intervals (2nds, 7ths and 4ths) are probibited, as are
are parallel and similar motion of perfect intervals (5ths and octaves).
The latter is encoded in Agda as follows.

@@

The music must also end with a cadence, which is a final motion from
the second or seventh degree to the tonic (first degree). These rules
are encoded in the following type, whose terms are exactly valid
first-species counterpoint.

@@

Explicit conversions from \texttt{PitchInterval} (which ensures
the inteval is not dissonant) to the general \texttt{Interval} have
been omitted in the listing above.
Note that \texttt{motionOk} is an implicit argument of the cons
constructor, and is able to be resolved automatically by the type checker,
and thus the proof does not need to be supplied by the user. Valid
first-species counterpoint can thus be written very naturally as
in the following simple example.

>>>>

Let us briefly explain how to implement the rule system of 
first-species counterpoint\footnote{The code is available at
\url{https://github.com/halfaya/MusicTools/blob/master/agda/Counterpoint.agda}.}.
In this exercise, we pick a base melody (the \emph{cantus firmus}),
and contruct a counterpoint melody note-by-note in the same rhythm.
The two voices are represented as a list of pitch-interval pairs,
where intervals must not be dissonant ones (2nds, 7ths, or 4ths).

\begin{lstlisting}
data IntervalQuality : Set where
  min3  : IntervalQuality
  maj3  : IntervalQuality
  per5  : IntervalQuality
  min6  : IntervalQuality
  maj6  : IntervalQuality
  per8  : IntervalQuality
  min10 : IntervalQuality
  maj10 : IntervalQuality

PitchInterval : Set
PitchInterval = Pitch × IntervalQuality
\end{lstlisting}

In a counterpoint list, there must not be perfect intervals 
(5ths and octaves) resulted from parallel or similar motion.
Therefore, we define a predicate that checks whether a motion 
is allowed or not.

@@

The last requirement is that the music must end with a cadence,
 which is a final motion from the 2nd or 7th degree to the tonic 
(1st degree). 
We impose this requirement by declaring two cadence constructors 
as the base cases of counterpoint.
Thus, we arrive at the following datatype for well-typed counterpoint\footnote{
For readability, we have ommited explicit conversions 
from \texttt{PitchInterval} (which ensures the interval is not dissonant) 
to the general \texttt{Interval}.}.

@@

\noindent Observe that \texttt{motionOk} is an implicit argument of 
the \texttt{\_::\_} constructor. 
The argument can be resolved automatically by the type checker,
hence there is no need to manually supply this proof.

Now, we can write valid first-species counterpoint as in the 
example below.
